---
output: html_document
params:
  instrumentName: NA
  dateRange: NA
  polarity: NA
  msLevel: NA
  intenHist: NA
  intenTrend: NA
  mzHist: NA
  mzTrend: NA
  resHist: NA
  resTrend: NA
  intenType: NA
  mzType: NA
---

```{r, echo=FALSE}
intenTypes <- c("cps" = "intensity_cps",  "relative" = "intensity_rel", "corrected" = "intensity_corr_cps")
mzTypes <- c("mDa" = "mDa_error_after_cal", "ppm" = "ppm_error_after_cal")
```


# Performance Report `r params$instrumentName`
*`r format(Sys.time(), "%Y-%m-%d %H:%M")`*

**Start:** `r format(params$dateRange[1], "%Y-%m-%d %H:%M")` | **End** `r format(params$dateRange[2], "%Y-%m-%d %H:%M")` (*latest*) | `r params$msLevel`-`r params$polarity`

#### Trend and distribution of average intensities (type: `r names(intenTypes[intenTypes == params$intenType])`)
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot1t <- params$intenTrend
plot1t <- plot1t + theme_grey(10) + theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)
plot1t
```
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot1d <- params$intenHist
plot1d <- plot1d + theme_grey(10) 
plot1d
```

#### Trend and distribution of average m/z shifts (type: `r names(mzTypes[mzTypes == params$mzType])`)
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot2t <- params$mzTrend
plot2t <- plot2t + theme_grey(10) + theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)
plot2t
```
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot2d <-params$mzHist
plot2d <- plot2d + theme_grey(10)
plot2d
```

#### Trend and distribution of average resolutions
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot3t <- params$resTrend
plot3t <- plot3t + theme_grey(10) + theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)
plot3t
```
```{r, echo=FALSE, fig.width=10, fig.height=1.5}
plot3d <-params$resHist
plot3d <- plot3d + theme_grey(10)
plot3d
```

